IS Studies on Social Network

### 2025-04-22 ProjectBlog/paper2/Network Paper/p2literature.qmd
CHITA

---
title: "IS Studies on Social Network"
date: 02/04/2025
date-modified: last-modified
draft: true
date-format: full
categories: [Others]
#image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
---

>>>>

---
title: "IS Studies on Social Network"
date: 02/04/2025
date-modified: last-modified
draft: false
date-format: full
categories: [Others]
#image: "search.png"
tbl-colwidths: [5,50,75]
format: 
  html:
    page-layout: full
---
